\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-05-01 ase20/intro.tex
Updated numbers in Intro

Our contribution is \( \tool \), a JavaScript IR-based Semantics Extraction
Toolchain:
\begin{itemize}[leftmargin=0.5cm]
  \item \textbf{\( \tool \) is the \textit{first tool that automatically
    extract} IR-based semantics from a language specification, ECMAScript.}
    For syntax, we formally introduce a variant of EBNF, \( \bnfes \),
    and propose a parser generation technique with
    lookahead parsing for \( \bnfes \), which supports automatic semicolon
    insertion. For semantics, we propose semi-automatic synthesis of AST-IR
    translators assisted by compile rules.  Compile rules describe
    how to convert each step of abstract algorithms into our intermediate
    representation \( \ires \) designed for ECMAScript. We evaluated \( \tool \)
    with the four most recent ECMAScript versions (ES7 to ES10).   \( \tool \)
    automatically generated parsers for all versions, and automatically compiled
    \inred{XX.X}\% of the steps in abstract algorithms on average.
  \item \textbf{\( \tool \) bridges gaps between the specification written in a
    natural language and tests.}
    To evaluate the correctness of \( \tool \), we checked the extracted
    semantics with the official test conformance suite, Test262~\cite{test262}.
    By manually completing missing parts of the AST-IR translator for the latest
    ECMAScript (ES10, 2019), we defined the \textit{first IR-based formal
    semantics of modern JavaScript}. It failed for \inred{XXXX} tests because of
    specification errors in ES10. Using the tests, we found eight specification errors,
    three of which had not been reported before. They were all confirmed by
    TC39 and will be fixed in the next release.  After fixing them, the formal
    semantics passed all \inred{XX,XXX} applicable tests.
  \item \textbf{\( \tool \) is also \textit{forward compatible} with new
    language features proposed for future ECMAScript specifications.}
    We evaluated the forward compatibility of \( \tool \) by applying it to all
    \inred{X} proposals that are ready for inclusion in the next ECMAScript
    (ES11, 2020).  It automatically synthesized parsers and compiled \inred{XXX}
    out of \inred{XXX} algorithm steps for all the proposals.  After completion
    of the missing parts, we found \inred{X} specifications errors by executing
    the corresponding tests in Test262.  After fixing them, the extracted
    semantics passed all \inred{XXX} tests.
\end{itemize}

>>>>

Our contribution is \( \tool \), a JavaScript IR-based Semantics Extraction
Toolchain:
\begin{itemize}[leftmargin=0.5cm]
  \item \textbf{\( \tool \) is the \textit{first tool that automatically
    extract} IR-based semantics from a language specification, ECMAScript.}
    For syntax, we formally introduce a variant of EBNF, \( \bnfes \),
    and propose a parser generation technique with
    lookahead parsing for \( \bnfes \), which supports automatic semicolon
    insertion. For semantics, we propose semi-automatic synthesis of AST-IR
    translators assisted by compile rules.  Compile rules describe
    how to convert each step of abstract algorithms into our intermediate
    representation \( \ires \) designed for ECMAScript. We evaluated \( \tool \)
    with the four most recent ECMAScript versions (ES7 to ES10).   \( \tool \)
    automatically generated parsers for all versions, and automatically compiled
    95.03\% of the steps in abstract algorithms on average.
  \item \textbf{\( \tool \) bridges gaps between the specification written in a
    natural language and tests.}
    To evaluate the correctness of \( \tool \), we checked the extracted
    semantics with the official test conformance suite, Test262~\cite{test262}.
    By manually completing missing parts of the AST-IR translator for the latest
    ECMAScript (ES10, 2019), we defined the \textit{first IR-based formal
    semantics of modern JavaScript}. It failed for \inred{XXXX} tests because of
    specification errors in ES10. Using the tests, we found eight specification errors,
    three of which had not been reported before. They were all confirmed by
    TC39 and will be fixed in the next release.  After fixing them, the formal
    semantics passed all 18,064 applicable tests.
  \item \textbf{\( \tool \) is also \textit{forward compatible} with new
    language features proposed for future ECMAScript specifications.}
    We evaluated the forward compatibility of \( \tool \) by applying it to all
    nine proposals that are ready for inclusion in the next ECMAScript
    (ES11, 2020).  It automatically synthesized parsers and compiled \inred{XXX}
    out of \inred{XXX} algorithm steps for all the proposals.  After completion
    of the missing parts, we found four specifications errors in BigInt
    proposal by executing the corresponding tests in Test262.  After fixing
    them, the extracted semantics passed all \inred{XXX} tests.
\end{itemize}
